---
output: 
  github_document:
    html_preview: true
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  fig.align = "center",
  comment   = "#>"
)

knitr::opts_chunk$set(
  echo      = TRUE)

```

## **{migratr}**

A set of tools for unifying **{sf}** and **{igraph}** object for geospatial network analysis.

## Install

First, if you haven’t done so, install `remotes`:

```{r, eval=FALSE}
install.packages("remotes")
```

Proceed to install **{migratr}** from Github:
```{r, eval=FALSE}
remotes::install_github("cjcallag/migratr")
```

## Example: All Populations

The goal is to create representations of network both projected over a map or as a sociogram. Because the network is the unit of analysis, the functions are designed to work with both a edge and node list.

First, load the package and any other tools you may require (I suggest using **{tidyverse}** tools for data manipulation):
```{r, warning=FALSE, message=FALSE}
library(migratr)
library(tidyverse)
```

Now load the sample node and edge lists:
```{r}
edges <- migratr::edgelist
nodes <- migratr::nodelist
```

  - Edges list: A `data.frame` containing a symbolic edge list in the first two columns. Additional columns are considered as edge attributes.
```{r}
glimpse(edges)
```

  - Nodes list: A `data.frame` and `sf` class object with node metadata. The first column will be assumed to contain the symbolic vertex names. 
```{r}
glimpse(nodes)
```

Using the edge and node list produce a new object with relationships and geographic data:

```{r, message=FALSE, warning=FALSE}
migratr_object <- migratr::get_proto_graph(edges = edges[edges["edge_type"] == "Adjacency/Population",],
                                           nodes = nodes)
migratr_object
```

Plot `migratr_object`:
```{r}
plot(migratr_object)
```


## Example: The Kurds

Load required data:
```{r}
edges <- migratr::kurds_edgelist
glimpse(edges)
nodes <- migratr::kurds_nodelist
glimpse(nodes)
```

Using the edge and node list produce a new object with relationships and geographic data:

```{r, message=FALSE, warning=FALSE}
migratr_object <- migratr::get_proto_graph(edges = edges,
                                           nodes = nodes)
migratr_object
```

Plot `migratr_object`:
```{r}
plot(migratr_object)
```
